% TO DO
% abbreviations
% future research questions!!
% finish literature review -- figures and table
% write abstract
% word count per chapter X
% revise chapter 3 and 4

\documentclass[11pt]{report}
\usepackage{graphicx}
\usepackage[margin = 2.5cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage{setspace}
\usepackage{tikz}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{verbatim}
\usepackage{lscape}

% checkmarks
\def\checkmark{\tikz\fill[scale=0.4](0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;} 

% fancy chapter headers
\usepackage{titlesec, blindtext, color}
\definecolor{gray75}{gray}{0.75}
\newcommand{\hsp}{\hspace{20pt}}
\titleformat{\chapter}[hang]{\Huge\bfseries}{\thechapter\hsp\textcolor{gray75}{|}\hsp}{0pt}{\Huge\bfseries}

% captions
\usepackage[labelfont=bf]{caption}
\captionsetup{skip=7pt, font=footnotesize} %,font={stretch=1}

% tables
\usepackage{multirow}
%\usepackage{longtable} 
\usepackage{array}
%\usepackage{verbatim} 
\usepackage{csvsimple}

% clinkable links 
\usepackage[hidelinks]{hyperref}
\hypersetup{
    colorlinks=false, %set true if you want colored links
    linktoc=all     %set to all if you want both sections and subsections linked
    %linkcolor=blue,  %choose some color if you want links to stand out
}

% Bibliography
\usepackage[backend=bibtex, natbib=true, url=false, doi=true, isbn=false, style=authoryear-comp, eprint=false, maxbibnames= 20, firstinits=true, maxcitenames=2]{biblatex}
\addbibresource{library2.bib}
\input{biblatex_options.tex}

\setlength\bibitemsep{1.5\itemsep}
% Numbering biblio
\usepackage[numbib,nottoc]{tocbibind}

% For tables from csv
\usepackage{csvsimple}



% line spacing
\renewcommand{\baselinestretch}{1.5}

%Line numbering
\usepackage{lineno}
%\linenumbers


\usepackage{moreverb} % for verbatim ouput

\begin{document}

\input{Title_page}

%\maketitle

% Declarations and acknowledgements here

\chapter*{Abstract}
This report summarises the work I have achieved throughout the first year of my PhD thesis at the Center for Biodiversity and Environment Research at UCL. Many experts state we have entered a new geological epoch, the Anthropocene, characterised by increasing impacts of human activities on the Earth's systems. Since the industrial revolution in the 18$^{\text{th}}$ century, anthropogenic activities have triggered global changes of planetary climate, and have led to the destruction and alteration of the natural habitat of many species. 

The impacts on global biodiversity have been dramatic. Vertebrate populations have globally declined by 60\% since 1970. Conserving biodiversity is not just a moral obligation. Biodiversity sustain important ecological processes that participate in making the planet habitable by humans. In order to put into place efficient conservation measures, it is vital to understand how different species cope with anthropogenic disturbances. Particularly, understanding what makes species sensitive to anthropogenic threats is valuable to conservation planning.

In the first Chapter, I present how trait-based approaches can be used to understand how species respond to disturbances, and how anthropogenic changes alter the composition of vertebrate communities. After exposing the gaps in our current understanding, I briefly detail the questions I tackled in this report. The second Chapter focuses on the collection of trait data across terrestrial vertebrates. These data were used in the third Chapter, which investigates how global land-use change impacts the functional diversity of local vertebrate communities. Finally, the last Chapter presents research questions I aim to tackle in the future years of my PhD.

\vspace{1cm}
\textbf{Key words:} vertebrates; traits; missing values imputation; land-use change; functional diversity.


% CONTENTS
\clearpage
\tableofcontents

%\cleardoublepage
\addcontentsline{toc}{section}{List of Tables}

\clearpage
\listoftables
\addcontentsline{toc}{section}{List of Figures}

%\clearpage
\listoffigures

% \clearpage
% List of abbreviations
%\addcontentsline{toc}{section}{List of abbreviations}


\chapter*{List of abbreviations}
\input{Abbreviations}

\clearpage
\addcontentsline{toc}{chapter}{Introduction}
\chapter*{Introduction}
\input{Chapters/Introduction}

\chapter{Literature review and hypotheses for the present work}
\input{Chapters/Chapter1}



\pagebreak
\chapter{Collecting and imputing ecological trait data across terrestrial vertebrates}
\input{Chapters/Chapter2}

\chapter{Global land-use change promotes the functional homogenisation of local  vertebrate communities}
\input{Chapters/Chapter3}

\chapter{Future questions}
\input{Chapters/Chapter4}

\clearpage
\chapter*{Bibliography}
\renewcommand{\baselinestretch}{1}
\printbibliography[heading=none]


\end{document}